Comparing MTurk and the US Population's Occupational Diversity

### 2018-11-28 Manuscript.Rmd
Added data source for 2015

require(ggplot2)
ggplot(barplot_data, aes(Occ_Nums, Values, fill = Group)) + 
  geom_errorbar(limits, position = dodge,
                width = 0.10, size = 1.0) +
  geom_col(position = dodge)  +
  ggtitle("MTurk's Occupational Diveristy with Error Bars") +
  labs(x = "Occupation", y = "Frequency") +
  theme(legend.position = "top", plot.title = element_text(hjust = 0.5), 
        text=element_text(family="serif"))+
  coord_flip()
```
##2015 Demographic Analysis 
##Study 1 Age
```{r}
#Chris's 2015 age analysis 
require(dplyr)

>>>>

require(ggplot2)
ggplot(barplot_data, aes(Occ_Nums, Values, fill = Group)) + 
  geom_errorbar(limits, position = dodge,
                width = 0.10, size = 1.0) +
  geom_col(position = dodge)  +
  ggtitle("MTurk's Occupational Diveristy with Error Bars") +
  labs(x = "Occupation", y = "Frequency") +
  theme(legend.position = "top", plot.title = element_text(hjust = 0.5), 
        text=element_text(family="serif"))+
  coord_flip()
```
##2015 Demographic Analysis 
##Study 1 Age
```{r}
#2015 Study 1 data
MTurk15 <- read.csv("~/MTurkOccDiversity/Demographics.csv", stringsAsFactors = FALSE)
names(MTurk15) <- c("country", "country text", "age", "gender", "years of current employment", "education level", "is english your primary language", "job title", "job title 2", "part time or full time", "sector", "employment status", "is MTurk primary income", "income currency", "approx annual income", "work hours per week", "ethnicity", "none")

#Chris's 2015 age analysis 
require(dplyr)
require(readxl)
